\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}
\usepackage[margin=1.4cm]{geometry}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.15in}
\addtolength{\textwidth}{0.3in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{0pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%----------HEADING----------
\begin{center}
    {\Large \scshape MOHAMMAD MAHTAB KHAN} \\[2mm]
    \footnotesize \raisebox{-0.1\height}
    \faPhone\ \underline{(403)714-9366} ~ 
    {\faEnvelope\  \underline{mahtabukhan16@gmail.com}} ~ 
    {\faLinkedin\ \underline{linkedin.com/in/mmahtabkhan}}  ~
    {\faGithub\ \underline{github.com/Mmahtab10}}
    \vspace{-8pt}
\end{center}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
    \resumeSubheading
      {University of Calgary}{Sep 2019 -- Apr 2024}
      {Bachelor of Science, Software Engineering}{Calgary, Alberta}
    \resumeItemListStart
    \resumeItem{CGPA: 3.8/4.0}
    \resumeItem{Dean's Honours List 2019-2022}
    \resumeItem{Ranked Top 10 in Bay Area Hacks 2020, Calgary Hacks 2020 and 2021, and SEC Hackathon UCalgary 2020}
    \resumeItem{Relevant Coursework: Distributed Systems, Data Science for Engineers, Database Management Systems, Software Performance Evaluation, TensorFlow for Deep Learning, Big Data Analysis, and Statistics.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

\
%-----------Experience---------------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Pason Systems}{May 2022 -- Aug 2023}
{Data Science Intern (Applied Research Team)}{Calgary, Alberta}
\resumeItemListStart
\resumeItem{Managed the development and maintenance of high-scale data analysis software, serving over 2000 weekly users and providing critical functionality for daily business operations.}
\resumeItem{Spearheaded the creation and deployment of section detection algorithms for industrial process sensors, improving data processing speed by 17\% and accuracy by 15\%.}
\resumeItem{Implemented K-means clustering algorithms to analyze patterns in drilling surfaces.}
\resumeItem{Enhanced performance analysis by 20\% and boosted critical event detection by 22\% through sensor data analytics.}
\resumeItem{Actively collaborated with product managers, designers, and sales representatives to gather requirements and generate client reports, ensuring daily project alignment and effective communication.}
\resumeItemListEnd

\resumeSubheading
{University of Calgary}{Jun 2021 -- Aug 2021}
{Software Engineering Research Intern}{Calgary, Alberta}
\resumeItemListStart
\resumeItem{Researched video data analytics for human biometrics, focusing on advanced action detection and accurate breathing rate estimation.}
\resumeItem{Led the development of user-friendly interfaces for agent-based modeling, enhancing accessibility for interdisciplinary teams.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects} 
\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{Sign4Good (Bay Area Hacks)} - Machine Learning Model for Hand Gesture to Text Translation}{Jul 2020}
\resumeItemListStart
\resumeItem{Developed a machine learning model using hand-tracking software to record gestures and convert them to plain text through a neural network.}
\resumeItem{Utilized Python libraries including Keras, OpenCV, and TensorFlow to achieve high validation scores.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Traffic Crash Prediction} - Data Analysis and Machine Learning Project}{Sep 2023 - Dec 2023}
\resumeItemListStart
\resumeItem{Led a project on traffic crash prediction using Databricks, handling over 700,000 records for data extraction, cleaning, and analysis.}
\resumeItem{Developed a predictive random forest model using PySpark, achieving high validation scores in forecasting accident variables.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{TrapEase} - Cybersecurity Capstone Project}{Sep 2023 - Present}
\resumeItemListStart
\resumeItem{Focused on enhancing cybersecurity through the development of decoy portals to attract and identify threats.}
\resumeItem{Utilized AWS services for hosting, database management, and advanced data visualization.}
\resumeItem{Adopted agile methodologies for rapid development and continuous improvement of the software.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\small{
\item{\textbf{Languages}{: Python, SQL, Spark, AWS, JSON} \\[1mm]}
\item{\textbf{Tools/Platforms}{: VS Code, GitHub, Docker, PowerBI, JIRA} \\[1mm]}
\item{\textbf{Libraries/Frameworks}{: ML libraries (e.g., TensorFlow, Keras), AWS Services (EC2, RDS, QuickSight)} \\ [1mm]}
}
\end{itemize}

%-----------INTERESTS & HOBBIES-----------
\section{Interests \& Hobbies}
\begin{multicols}{2}
\begin{itemize}
\item Basketball
\item Soccer
\item Golf
\item Hockey
\item E-sports
\item Table Tennis
\end{itemize}
\end{multicols}

\end{document}
